%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{tikz}


\begin{document}


%%%%%%%%%%%%%%%%%%%%
%    2022-11-09
%%%%%%%%%%%%%%%%%%%%

\namesection{Ehsan}{Salimi}{

\href{https://www.linkedin.com/feed/}{\faIcon{linkedin} Ehsan Salimi |} 
\href{https://github.com/EhsanSl}{ \faIcon{github} EhsanSl |} 
\href{mailto:esalimi.cs@gmail.com}{ \faIcon{envelope} Esalimi.cs@gmail.com}
%\href{https://ehsansl.github.io}{ \faIcon{user} Portfolio } 
}



%%%%%%%%%%%%%%%%%%%%%
%    Educations
%%%%%%%%%%%%%%%%%%%%%

\sectionsep
\section{Education}

\descript{University of Windsor}
\runsubsection{| BS.c in Computer Science (HONOURS)}
\location{| Minor in Mathematics}
\location{| Major GPA: 90/100 | \faIcon{map-marker} Windsor , CA \textbullet{} 
Expected APR 2024}
\location{| Dean's Office Scholarship Recipient, Fall 2020 and Winter 2021}
\location{| Member of Golden Key International Honour Society}
\sectionsep
\descript{York dale High School}
\runsubsection{|OSSD }
\location{Finished JUN 2020| \faIcon{map-marker} Toronto, CA \textbullet{} GPA: 87.5/100}



\sectionsep
\section{Experience}
\runsubsection{Research Assistant}
\descript{| Data analysis | Machine Learning |Dr. Arunita Jaekel and Dr. Hossein Fani }
\location{June 2022 - Present | \faIcon{map-marker} Windsor, ON, Ca}
 
\begin{tightemize}
\large{
\item The main focus of the activity is implementing Machine learning algorithms to train prediction models and data cleaning in an efficient and precise manner.
\item Developed prediction models to discriminate between accurate signals sent between automated cars and signals that are malicious or erroneous.
}
\end{tightemize}
\sectionsep


\runsubsection{Teaching Assistant}
\descript{| Computer Architecture | Python  }
\location{Sep 2021 - Present | \faIcon{map-marker} Windsor, ON, CA}

\begin{tightemize}
\large{
\item Weekly office hours and lab sessions for students to discuss their problems. My responsibilities also include marking students' exams and assignments.
\end{tightemize}

\sectionsep
\runsubsection{Gallery Administrative Assistant}
\descript{| Volunteer | Art Gallery of Windsor }
\location{ May 2021 - Sep 2021 | \faIcon{map-marker} Windsor, CA }
\begin{tightemize}
\large{
\item Creating and developing a surveying tool. Conduct research and surveys of community institutions.
\item Receiving and recording screening documents for program registrations. External groups monitor and analyse community trends (Ie. WECHU). Making a list of best practises that have been documented.
}
\end{tightemize}



\sectionsep
\section{Recent Projects}
\runsubsection{Machine Learning and AI}
\location{Technologies used: Python}
\begin{tightemize}
\large{
\item Developing prediction models based on data sets in the field of automated vehicles, as well as attacks aimed at stifling the evolution and development of this mode of transportation.
\item Developing models to create a baseline for detecting predatory conversations on online platforms.
}
\end{tightemize}
\sectionsep

\runsubsection{Discord Bot}
\location{Technologies used: Python, Flask, Open Weather API}
\begin{tightemize}
\large{
\item Developing a Discord bot for server management, which includes chat and member monitoring, as well as interactive utilities like weather forecasts.
}
\end{tightemize}

\section{Skills}
\runsubsection{Programming \& Web Development}
\runsubsection\location{\runsubsection\textbullet{\textbullet{\textbullet{\textbullet{Python}}}}
\textbullet{}\runsubsection\textbullet{}\textbullet{Java }
\textbullet{\runsubsection\textbullet{\textbullet{MySQL }}}
\textbullet{\runsubsection\textbullet{\textbullet{HTML }}}
\textbullet{}\runsubsection\textbullet{\textbullet{CSS }}
\textbullet{}\runsubsection\textbullet{C }
\textbullet{}\runsubsection\textbullet{\LaTeX }  
\textbullet{PHP }
\textbullet{Js}
}


\sectionsep
\runsubsection{Systems, tools \& apps}
\runsubsection \location{  
\textbullet{}\runsubsection\textbullet{}\textbullet{}Linux
\textbullet{}\runsubsection\textbullet{}\textbullet{}Git
\textbullet{}\runsubsection\textbullet{}Visual Studio
\textbullet{}\runsubsection\textbullet{}Bash
\runsubsection\textbullet{APIs}

}

\sectionsep
\runsubsection{Core Skills}
\runsubsection \location{  \textbullet{} Agile Method
\textbullet{}DevOps 
\textbullet{}Data Structures and Algorithms
\textbullet{}Unified Process
\textbullet{Object-Oriented Analysis/Programming }
\hspace{1cm}
\textbullet{}Unit Testing
\textbullet{}Problem Solving
\textbullet{}Collaboration and Teamwork
\textbullet{}Communication
}





\sectionsep\sectionsep\sectionsep\sectionsep\sectionsep\sectionsep
\end{document}  \documentclass[]{article}